---
title: "Plot assignment"
author: "Template: Ian Hussey; content: [Student name]"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

# Dependencies

```{r}

library(tidyverse)
library(janitor)
library(ggthemes)
library(reshape2)
```

# Instructions

possible data sources:
  - osf.io
  - AIID dataset: https://osf.io/pcjwf/ -> confirmatory dataset

The goal of this exercise is to produce both good and bad examples of plots *and to be explicit about what makes them good or bad*. 

The data can be real or fabricated. The plots can convey realistic or silly messages - but they must convey them clearly. You can get real data from many sources. A good one is the open science framework (osf.io). You can also simply make up data, either by hand or using simulation functions (e.g., `rnorm`) or the many simulation packages. If simulating data, ensure that you (a) use set.seed() to make it reproducible, and (b) save a copy of the final data that you're using to disk and then reload it in the script so that the plot is reproducible.

The goal is neither to reproduce the types of plots that you most often see in journals (bar plots, etc.) nor to use a very fancy looking plot just for the sake of it - if it is very unlikely that you'd ever be able to use the plot to convey a research finding in an article, blog, poster, tweet, infographic or otherwise, it's probably not a good choice either.

The plots must be reproducible. Provide the data as well as the code to reproduce them. The plots should also be saved as individual images (pdf or png).

Under each plot, here in the RMarkdown, briefly explain what types of analysis the plot is suitable for, what elements of the results the plot attempts to clearly convey. For the bad plot, do the opposite: emphasize what features of the results the plot obscures or makes unclear. In doing so, communicate to me that you understand what makes a good plot to convey the results of quantitative analyses to viewers.

Consider making use of the many extensions to ggplot2, e.g.:

- https://r-graph-gallery.com
- https://krzjoa.github.io/awesome-r-dataviz/#/
- ggdist https://mjskay.github.io/ggdist/
- ggrepel
- ggpubr
- see
- ggsignif
- and others: https://exts.ggplot2.tidyverse.org/gallery/

# Data

```{r}
# Load the dataset
data <- read.csv("births-and-deaths-projected-to-2100.csv") |>
  clean_names()
```

# Good plot

```{r}

# Select specific countries
selected_countries <- c("Switzerland", "Ireland", "Germany", "France", "Italy", 
                        "United States", "China", "India", "Brazil", "Australia", 
                        "Least developed countries", "More developed regions", 
                        "Less developed regions", "excluding least developed countries")

# Filter the data for the selected countries
filtered_data <- filter(data, entity %in% selected_countries)

# Splitting the dataset into historical and projected
historical_data <- filtered_data %>% 
  filter(year <= 2021) %>%
  select(entity, year, births_sex_all_age_all_variant_estimates, deaths_sex_all_age_all_variant_estimates)

projected_data <- filtered_data %>% 
  filter(year >= 2022) %>%
  select(entity, year, births_sex_all_age_all_variant_medium, deaths_sex_all_age_all_variant_medium)

# Renaming columns for consistency
names(historical_data)[3:4] <- c("births", "deaths")
names(projected_data)[3:4] <- c("births", "deaths")

# Combining historical and projected data
combined_data <- bind_rows(historical_data, projected_data)

# Reshaping the data for plotting
data_long <- combined_data %>%
  pivot_longer(cols = c("births", "deaths"),
               names_to = "type",
               values_to = "value")

# Assuming data_long is your dataset prepared earlier
# Aggregate global data
global_data <- data_long %>%
  group_by(year, type) %>%
  summarize(value = sum(value, na.rm = TRUE)) %>%
  mutate(entity = "Global")

# Append global data to the original dataset
combined_data <- bind_rows(data_long, global_data)

# Adjust the factor levels to make 'Global' the first level
combined_data$entity <- fct_relevel(combined_data$entity, "Global")

# Create the faceted plot
gp <- ggplot(combined_data, aes(x = year, y = value, color = type)) +
  geom_line() +
  facet_wrap(~entity, scales = "free_y", nrow = 4) + # Adjust nrow for better layout
  labs(title = "Historical and Projected Births and Deaths (1950-2100)",
       x = "Year",
       y = "Count",
       color = "Type") +
  theme_clean() +
  theme(legend.position = "bottom")

# Print the plot
gp


```

This facet wrap plot is good because you can see both the death and births that occurred from 1950 until 2021 and the projected deaths and birth from 2022 until 2100 for the selected countries (some have been grouped) and the global figures. The plot also makes it easy to compare between countries and regions or against the global growth/decline. What is clear is that at one point all births will be less than the deaths and that form that point on the population will shrink. This can be done for countries or just some of interest by changing or adding names to selection


```{r}
library(plotly)

# interactive plot
g <- ggplot(combined_data, aes(x = year, y = value, color = entity, linetype = type)) +
  geom_line() +
  labs(title = "Historical and Projected Births and Deaths (1950-2100)",
       x = "Year",
       y = "Count",
       color = "Country",
       linetype = "Type") +
  theme_minimal() +
  theme(legend.position = "bottom")

# Convert to an interactive plotly object
interactive_plot <- ggplotly(g)

# Display the interactive plot
interactive_plot
```

I also made an interactive plot. This plot is great because you can zoom on either the y or x axis and the problem of the lines overlapping each other is pretty much solved. Additionally you can hover with the mouse over the lines and you will receive information about the country you are and at what point in time and the count of that spot. The use of this plot is very intuitive in my opinion. It just too bad that you can't save it.

# Bad plot

```{r}
# worse
bp <- ggplot(combined_data, aes(x = year, y = value, color = type)) +
  geom_line() +
  facet_wrap(~entity, scales = "free_y", nrow = 10) +
  scale_color_manual(values = rep("black", 2)) + # Single colour for all lines
  scale_x_continuous(breaks = seq(1950, 2100, 25), labels = rep("", length(seq(1950, 2100, 25)))) + 
  scale_y_continuous(labels = function(x) paste0("$", x/1000, "K")) + 
  labs(x = "Random Time Units", y = "Arbitrary Values", color = "Random Categories") +
  guides(color = guide_legend(reverse = TRUE)) + # Reversed legend
  theme_minimal() +
   theme(text = element_text(size = 1, color = "magenta"),
        plot.title = element_text(face = "bold", color = "orange"),
        panel.grid.major = element_line(size = .5, linetype = 'dotted', color = "red"),
        panel.grid.minor = element_line(size = .5, linetype = 'dotted', color = "red"),
        axis.text.x = element_text(angle = 190, vjust = 0.5, hjust=1),
        legend.position = c(0.5, 0.5),
        legend.background = element_rect(fill = "black"),
        strip.text.x = element_text(color = "blue", face = "italic")) # Misleading facet labels

# print
bp


```

This plot is bad for multiple reasons. First there is no title so its hard to know what it is about. the lines in the plot are the same colour so one doesn't know which line is births and which is deaths. the lines for the y-axis aren't straight and a distracting red colour and the legend is in the middle of the plot covering part of some plots. It is also black making only the purple text on it visible. The labs for x and y are confusing as are the number for the y axis. the x axis is non existent and thus there is loss of information and one can't distinguish between historical and predictive figures. Furthermore, one can't read the title of the plots making it impossible to identify which plot belongs to which country. also the theme minimal makes the png hard to see if you laptop is on night mode.

# Write to disk

Write to disk as a .pdf or .png.

Name them "plot_good_[yourname]" and "plot_bad_[yourname]".

```{r}

# Saving good plot
ggsave("plot_good_SzukicsAndreas.png", gp, width = 20, height = 16)

# Saving bad plot
ggsave("plot_bad_SzukicsAndreas.png", bp, width = 20, height = 16)

```

# Session info

```{r}

sessionInfo()

```


