---
title: "Evaluations the relationship between the big-5 personality facets and implicit racial attitudes"
subtitle: "Analysis"
author: "Andreas Szukics"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
 html_document:
    # code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
    css: styles.css  # CSS file for costumized html
---

```{r, include=FALSE}

# set knit options
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

# disable scientific notation
options(scipen = 999) 

```

# Libraries

```{r, echo = FALSE}

library(tidyverse)
library(knitr)
library(kableExtra)
library(janitor)
library(ltm)
library(scales)
library(PupillometryR)
library(palmerpenguins)
library(ggdist)
library(ggExtra)
library(ggrepel)
library(remotes)
library(ggthemes)
library(ggsci)
# devtools::install_github("psyteachr/introdataviz")

```


# Data

## Load the processed data 

```{r, echo = FALSE}

# Loading data
data_processed <- read_csv("../data/processed/data_processed.csv")

```


# Descriptive tables

## Sample size before exclusions

```{r}

data_processed |>
  count(name = "n") |>
  kable() |>
  add_header_above(header = c("Whole sample" = 1)) |> # note that you can add header rows to tables like this. The "1" indicates the number of columns the header should span. The sum of these numbers must equal the number of columns or you'll get an error.
  kable_classic(full_width = FALSE)

```


## Dataframe without excluded subject

```{r}

# Loading only subject to be included
data_processed_after_exclusions <- data_processed |>
  filter(exclude_participant == "include")

```


## Sample size after exclusions

Sample used in subsequent analyses

```{r}

data_processed_after_exclusions |>
  count(name = "n") |>
  kable() |>
  add_header_above(header = c("For analysis" = 1)) |>
  kable_classic(full_width = FALSE)

```


## Age

```{r}

data_processed_after_exclusions |>
  mutate(age = as.numeric(age)) |>
  summarise(Mean = mean(age, na.rm = TRUE),
            SD = sd(age, na.rm = TRUE)) |>
  mutate_all(.funs = janitor::round_half_up, digits = 1) |>
  kable() |>
  add_header_above(header = c("Age" = 2)) |>
  kable_classic(full_width = FALSE)

```


## Gender

```{r}

data_processed_after_exclusions |> 
  rename(Gender = gender) |>
  group_by(Gender) |> 
  summarise(n = n()) |> 
  mutate(Percent = paste0(round_half_up((n / sum(n)) * 100, 1), "%")) |>
  mutate(Gender = stringr::str_to_sentence(Gender)) |> # Change the case of the Gender variable so that it prints nicely
  kable() |>
  kable_classic(full_width = FALSE)

```


# Descriptive statistics

## Cronbach alpha calculation

```{r}

# List of subscales
subscales <- c("a", "c", "e", "n", "o")
num_items <- c(9, 9, 8, 8, 10)

# Empty list to store Cronbach's alpha values
cronbach_alphas <- list()

# Loop to compute Cronbach's alpha for each subscale
for (i in seq_along(subscales)) {
    # Generate column names for the current subscale
    selected_columns <- paste0("bfi_", subscales[i], 1:num_items[i])
  
    # Filter rows where all items in the subscale are complete (no NAs)
    # Using a standard subsetting approach instead of all_of
    dat_subscale <- data_processed_after_exclusions[, selected_columns, drop = FALSE] |>
                    na.omit()

    # Check if the subscale has sufficient data for alpha calculation
    if(nrow(dat_subscale) > 1) {
        # Compute Cronbach's alpha
        alpha_subscale <- cronbach.alpha(dat_subscale)$alpha
    } else {
        alpha_subscale <- NA  # Assign NA if not enough data
    }
  
    # Store the alpha coefficient in the list
    cronbach_alphas[[subscales[i]]] <- alpha_subscale
}

# Print Cronbach's alpha values
print(cronbach_alphas)


```

# Plotting

## Histogramms

### BFI subscale

```{r}
# Theme for all plots
# theme_set()

#BFI A
ggplot(data_processed_after_exclusions, aes(x = mean_a)) +
  geom_histogram(position = "dodge",
                 binwidth = .1,
                 fill     = "lightblue",
                 color    = "black")+
  geom_density(alpha = 0.5, fill = "orange") +
  geom_vline(aes(xintercept = mean(mean_a, na.rm = TRUE)), 
             linetype = "dashed", color = "red", size = 1) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 15)) +
  coord_cartesian(xlim = c(1, 6), ylim = c(1, 15)) +
  labs(title           = "BFI mean score",
       subtitle        = "Subscale A",
       x               = "Mean score",
       y               = "Count") +
   theme_classic() +
  # Make the axis label bold
  theme(plot.title    = element_text(color = "#0099F8", size = 16, face = "bold"),
        plot.subtitle = element_text(size = 10, face = "bold"),
        axis.title.x  = element_text(face = "bold"),
        axis.title.y  = element_text(face = "bold"))

#BFI C
ggplot(data_processed_after_exclusions, aes(x = mean_c)) +
  geom_histogram(position = "dodge",
                 binwidth = .1,
                 fill     = "lightblue",
                 color    = "black")+
  geom_density(alpha = 0.5, fill = "orange") +
  geom_vline(aes(xintercept = mean(mean_c, na.rm = TRUE)), 
             linetype = "dashed", color = "red", size = 1) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 15)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 15)) +
  coord_cartesian(xlim = c(1, 6), ylim = c(1, 15)) +
  labs(title           = "BFI mean score",
       subtitle        = "Subscale C",
       x               = "Mean score",
       y               = "Count") +
   theme_test() +
  # Make the axis label bold
  theme(plot.title    = element_text(color = "#0099F8", size = 16, face = "bold"),
        plot.subtitle = element_text(size = 10, face = "bold"),
        axis.title.x  = element_text(face = "bold"),
        axis.title.y  = element_text(face = "bold"))

#BFI  E
ggplot(data_processed_after_exclusions, aes(x = mean_e)) +
  geom_histogram(position = "dodge",
                 binwidth = .1,
                 fill     = "lightblue",
                 color    = "black")+
  geom_density(alpha = 0.5, fill = "orange") +
  geom_vline(aes(xintercept = mean(mean_e, na.rm = TRUE)), 
             linetype = "dashed", color = "red", size = 1) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 15)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 15)) +
  coord_cartesian(xlim = c(1, 6), ylim = c(1, 15)) +
  labs(title           = "BFI mean score",
       subtitle        = "Subscale E",
       x               = "Mean score",
       y               = "Count") +
   theme_ggdist() +
  # Make the axis label bold
  theme(plot.title    = element_text(color = "#0099F8", size = 16, face = "bold"),
        plot.subtitle = element_text(size = 10, face = "bold"),
        axis.title.x  = element_text(face = "bold"),
        axis.title.y  = element_text(face = "bold"))

#BFI N
ggplot(data_processed_after_exclusions, aes(x = mean_n)) +
  geom_histogram(position = "dodge",
                 binwidth = .1,
                 fill     = "lightblue",
                 color    = "black")+
  geom_density(alpha = 0.5, fill = "orange") +
  geom_vline(aes(xintercept = mean(mean_n, na.rm = TRUE)), 
             linetype = "dashed", color = "red", size = 1) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 15)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 15)) +
  coord_cartesian(xlim = c(1, 6), ylim = c(1, 15)) +
  labs(title           = "BFI mean score",
       subtitle        = "Subscale N",
       x               = "Mean score",
       y               = "Count") +
   theme_clean() +
  # Make the axis label bold
  theme(plot.title    = element_text(color = "#0099F8", size = 16, face = "bold"),
        plot.subtitle = element_text(size = 10, face = "bold"),
        axis.title.x  = element_text(face = "bold"),
        axis.title.y  = element_text(face = "bold"))

#BFI O
ggplot(data_processed_after_exclusions, aes(x = mean_o)) +
  geom_histogram(position = "dodge",
                 binwidth = .1,
                 fill     = "lightblue",
                 color    = "black")+
  geom_density(alpha = 0.5, fill = "orange") +
  geom_vline(aes(xintercept = mean(mean_o, na.rm = TRUE)), 
             linetype = "dashed", color = "red", size = 1) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 15)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 15)) +
  coord_cartesian(xlim = c(1, 6), ylim = c(1, 15)) +
  labs(title           = "BFI mean score",
       subtitle        = "Subscale O",
       x               = "Mean score",
       y               = "Count") +
  theme_calc() +
  # Make the axis label bold
  theme(plot.title    = element_text(color = "#0099F8", size = 16, face = "bold"),
        plot.subtitle = element_text(size = 10, face = "bold"),
        axis.title.x  = element_text(face = "bold"),
        axis.title.y  = element_text(face = "bold"))


```


### IAT

```{r}

#IAT D
ggplot(data_processed_after_exclusions, aes(x = D)) +
  geom_histogram(position = "dodge",
                 binwidth = .05,
                 fill     = "lightblue",
                 color    = "black")+
  geom_density(alpha = 0.5, fill = "orange") +
  geom_vline(aes(xintercept = mean(D, na.rm = TRUE)), 
             linetype = "dashed", color = "red", size = 1) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 15)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 15)) +
  coord_cartesian(xlim = c(-1, .5), ylim = c(1, 15)) +
  labs(title           = "Implicit Association Test",
       subtitle        = "Greenwald \"D\" score",
       x               = "D score",
       y               = "Count") +
  theme_classic() +
  # Labs
  theme(plot.title    = element_text(color = "#0099F8", size = 16, face = "bold"),
        plot.subtitle = element_text(size = 10, face = "bold"),
        axis.title.x  = element_text(face = "bold"),
        axis.title.y  = element_text(face = "bold"))
```


# Data analysis tests

## Pearson's r correlation

\TODO add table of means, SDs, Ns

```{r}

# Ensuring the necessary columns are present in the data frame
required_columns <- c("D", "mean_a", "mean_c", "mean_e", "mean_n", "mean_o")
if(all(required_columns %in% names(data_processed_after_exclusions))) {
    # Calculating the correlation matrix
    correlation_matrix <- cor(data_processed_after_exclusions[required_columns], 
                              use = "pairwise.complete.obs", method = "pearson")

    # Rounding the correlation matrix to two decimal places
    correlation_matrix_rounded <- round(correlation_matrix, 2)

    # Formatting and printing the rounded correlation matrix as a table
    kable(correlation_matrix_rounded) %>%
    kable_classic(full_width = FALSE)
} else {
    cat("One or more required columns are missing from the data frame.")
}

```


## T-test

```{r}

# creating a new variable and encoding male and female
data_processed_after_exclusions$gender_numeric <- ifelse(data_processed_after_exclusions$gender == "male", 1, 0)

library(report)

model_D <- lm(D ~ gender_numeric, data = data_processed_after_exclusions)
report(model_D)

```


### Hypothesis tests

```{r}

# List of BFI subscales
subscales <- c("mean_a", "mean_c", "mean_e", "mean_n", "mean_o")

# Initialize a list to store models and their reports
model_reports <- list()

# Loop through each subscale and run a separate regression
for (subscale in subscales) {
  formula_str <- paste("D ~", subscale)
  model <- lm(as.formula(formula_str), data = data_processed_after_exclusions)
  
  # Generate the report for the model
  model_report <- report(model)
  
  # Store the model and its report in the list
  model_reports[[subscale]] <- list(model = model, report = model_report)
}

# Print the reports of each model
for (subscale in names(model_reports)) {
  cat("\nRegression with", subscale, "as predictor:\n")
  print(model_reports[[subscale]]$report)
}

```


More complex plots:

#### Scatter plots with regression lines

Label points using ggrepel: https://cran.r-project.org/web/packages/ggrepel/vignettes/ggrepel.html

\TODO Label the points in a scatter plot using their participant codes.

```{r}

# Example for BFI subscale 'mean_a'
ggplot(data_processed_after_exclusions, aes(x = mean_a, y = D)) +
  geom_point(aes(color = gender), alpha = 0.5) +  # Scatter plot
  geom_smooth(method = "lm", color = "blue", se = FALSE) +  # Regression line
  labs(title = "Relationship between the IAT and BFI subscale",
       x = "BFI Subscale A Score",
       y = "IAT D Score") +
  theme_minimal()

# Calculating the 10th and 90th percentiles of the IAT 'D' scores
lower_bound <- quantile(data_processed_after_exclusions$D, probs = 0.1)
upper_bound <- quantile(data_processed_after_exclusions$D, probs = 0.9)

# Creating a new variable to flag extreme scores
data_processed_after_exclusions <- data_processed_after_exclusions %>%
  mutate(extreme_score = ifelse(D <= lower_bound | D >= upper_bound, "Extreme", "Normal"))

# Scatter plot for BFI subscale 'mean_a'
ggplot(data_processed_after_exclusions, aes(x = mean_a, y = D)) +
  geom_point(aes(shape = extreme_score, color = gender)) +
  scale_shape_manual(values = c("Normal" = 16, "Extreme" = 17),
                     labels = c("Extreme Score", "Normal Score")) +  # Rename shape categories
  scale_color_manual(values = c("male" = "violet", "female" = "#0099F8"),
                     labels = c("Female", "Male")) +  # Rename color categories and specify colors
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 15)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) +
  coord_cartesian(xlim = c(1, 6), ylim = c(-1, .5)) +
  labs(title    = "Scatter plot for IAT prediction",
       subtitle = "Subscale A",
       x        = "Mean score",
       y        = "D",
       shape    = "Score Category",
       color    = "Gender") +
  theme_clean() +
  theme(plot.title    = element_text(color = "#0099F8", size = 16, face = "bold"),
        plot.subtitle = element_text(size = 10, face = "bold"),
        axis.title.x  = element_text(face = "bold"),
        axis.title.y  = element_text(face = "bold"),
        legend.position = "right")  

# Example for BFI subscale 'mean_c'
ggplot(data_processed_after_exclusions, aes(x = mean_c, y = D)) +
  geom_point(aes(color = gender), alpha = 0.5) +  # Scatter plot
  geom_smooth(method = "lm", color = "blue", se = FALSE) +  # Regression line
  labs(title = "Relationship between the IAT and BFI subscale",
       x = "BFI Subscale C Score",
       y = "IAT D Score") +
  theme_minimal()

# Scatter plot for BFI subscale 'mean_c'
ggplot(data_processed_after_exclusions, aes(x = mean_c, y = D)) +
  geom_point(aes(shape = extreme_score, color = gender)) +
  scale_shape_manual(values = c("Normal" = 16, "Extreme" = 17),
                     labels = c("Extreme Score", "Normal Score")) +  # Rename shape categories
  scale_color_manual(values = c("male" = "violet", "female" = "#0099F8"),
                     labels = c("Female", "Male")) +  # Rename color categories and specify colors
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 15)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) +
  coord_cartesian(xlim = c(1, 6), ylim = c(-1, .5)) +
  labs(title    = "Scatter plot for IAT prediction",
       subtitle = "Subscale C",
       x        = "Mean score",
       y        = "D",
       shape    = "Score Category",
       color    = "Gender") +
  theme_clean() +
  theme(plot.title    = element_text(color = "#0099F8", size = 16, face = "bold"),
        plot.subtitle = element_text(size = 10, face = "bold"),
        axis.title.x  = element_text(face = "bold"),
        axis.title.y  = element_text(face = "bold"),
        legend.position = "right")  

# Example for BFI subscale 'mean_e'
ggplot(data_processed_after_exclusions, aes(x = mean_e, y = D)) +
  geom_point(aes(color = gender), alpha = 0.5) +  # Scatter plot
  geom_smooth(method = "lm", color = "blue", se = FALSE) +  # Regression line
  labs(title = "Relationship between the IAT and BFI subscale",
       x = "BFI Subscale E Score",
       y = "IAT D Score") +
  theme_minimal()

# Scatter plot for BFI subscale 'mean_e'
ggplot(data_processed_after_exclusions, aes(x = mean_e, y = D)) +
  geom_point(aes(shape = extreme_score, color = gender)) +
  scale_shape_manual(values = c("Normal" = 16, "Extreme" = 17),
                     labels = c("Extreme Score", "Normal Score")) +  # Rename shape categories
  scale_color_manual(values = c("male" = "violet", "female" = "#0099F8"),
                     labels = c("Female", "Male")) +  # Rename color categories and specify colors
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 15)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) +
  coord_cartesian(xlim = c(1, 6), ylim = c(-1, .5)) +
  labs(title    = "Scatter plot for IAT prediction",
       subtitle = "Subscale E",
       x        = "Mean score",
       y        = "D",
       shape    = "Score Category",
       color    = "Gender") +
  theme_clean() +
  theme(plot.title    = element_text(color = "#0099F8", size = 16, face = "bold"),
        plot.subtitle = element_text(size = 10, face = "bold"),
        axis.title.x  = element_text(face = "bold"),
        axis.title.y  = element_text(face = "bold"),
        legend.position = "right")  

# Example for BFI subscale 'mean_n'
ggplot(data_processed_after_exclusions, aes(x = mean_n, y = D)) +
  geom_point(aes(color = gender), alpha = 0.5) +  # Scatter plot
  geom_smooth(method = "lm", color = "blue", se = FALSE) +  # Regression line
  labs(title = "Relationship between the IAT and BFI subscale ",
       x = "BFI Subscale N Score",
       y = "IAT D Score") +
  theme_minimal()

# Scatter plot for BFI subscale 'mean_n'
ggplot(data_processed_after_exclusions, aes(x = mean_n, y = D)) +
  geom_point(aes(shape = extreme_score, color = gender)) +
  scale_shape_manual(values = c("Normal" = 16, "Extreme" = 17),
                     labels = c("Extreme Score", "Normal Score")) +  # Rename shape categories
  scale_color_manual(values = c("male" = "violet", "female" = "#0099F8"),
                     labels = c("Female", "Male")) +  # Rename color categories and specify colors
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 15)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) +
  coord_cartesian(xlim = c(1, 6), ylim = c(-1, .5)) +
  labs(title    = "Scatter plot for IAT prediction",
       subtitle = "Subscale N",
       x        = "Mean score",
       y        = "D",
       shape    = "Score Category",
       color    = "Gender") +
  theme_clean() +
  theme(plot.title    = element_text(color = "#0099F8", size = 16, face = "bold"),
        plot.subtitle = element_text(size = 10, face = "bold"),
        axis.title.x  = element_text(face = "bold"),
        axis.title.y  = element_text(face = "bold"),
        legend.position = "right")  

# Example for BFI subscale 'mean_o'
ggplot(data_processed_after_exclusions, aes(x = mean_o, y = D)) +
  geom_point(aes(color = gender), alpha = 0.5) +  # Scatter plot
  geom_smooth(method = "lm", color = "blue", se = FALSE) +  # Regression line
  labs(title = "Relationship between the IAT and BFI subscale",
       x = "BFI Subscale O Score",
       y = "IAT D Score") +
  theme_minimal()

# Scatter plot for BFI subscale 'mean_o'
ggplot(data_processed_after_exclusions, aes(x = mean_o, y = D)) +
  geom_point(aes(shape = extreme_score, color = gender)) +
  scale_shape_manual(values = c("Normal" = 16, "Extreme" = 17),
                     labels = c("Extreme Score", "Normal Score")) +  # Rename shape categories
  scale_color_manual(values = c("male" = "violet", "female" = "#0099F8"),
                     labels = c("Female", "Male")) +  # Rename color categories and specify colors
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  # scale_x_continuous(breaks = scales::pretty_breaks(n = 15)) +
  # scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) +
  # coord_cartesian(xlim = c(1, 6), ylim = c(-1, .5)) +
  labs(title    = "Scatter plot for IAT prediction",
       subtitle = "Subscale O",
       x        = "Mean score",
       y        = "D",
       shape    = "Score Category",
       color    = "Gender") +
  theme_clean() +
  theme(plot.title    = element_text(color = "#0099F8", size = 16, face = "bold"),
        plot.subtitle = element_text(size = 10, face = "bold"),
        axis.title.x  = element_text(face = "bold"),
        axis.title.y  = element_text(face = "bold"),
        legend.position = "right",
        legend.box.background = element_blank())
```


## Combining plots

```{r}

# # install.packages("devtools")
# devtools::install_github("thomasp85/patchwork")


library(patchwork)

p1 <- ggplot(data_processed_after_exclusions, aes(x = gender, y = mean_evaluation, fill = gender)) +
  geom_boxplot(width         = 0.1,
               outlier.shape = NA,
               position      = position_nudge(x      = -0.2),
               alpha         = .7) +
  geom_point(position        = position_jitter(width = .1),
             aes(color       = gender),
             alpha           = .75,
             color           = "black",
             shape           = 21) +
  geom_flat_violin(trim=FALSE, alpha = 0.4,
  position = position_nudge(x = rain_height+.05)) +
  scale_y_continuous(breaks  = pretty_breaks(n = 7)) +
  coord_cartesian(ylim       = c(0, 7)) +
     scale_fill_discrete(name      = "Gender",
                      labels    = c("Female",
                                    "Male",
                                    "Non-Binary"))+
  labs(title                    = "Raincloud Plot",
       x                        = "Gender",
       y                        = "Mean Evalations")
  theme_minimal()
p2 <- ggplot(data_processed_after_exclusions, aes(x    = gender, y    = mean_evaluation, fill = gender)) +
  geom_flat_violin(draw_quantiles = .5,
              trim           = TRUE,
              alpha          = 0.5,) +
  scale_y_continuous(breaks  = pretty_breaks(n = 7)) +
  coord_cartesian(ylim       = c(0, 7)) +
   scale_fill_discrete(name      = "Gender",
                      labels    = c("Female",
                                    "Male",
                                    "Non-Binary"))+
  labs(title                    = "Violin Plot of Mean Evaluation",
       x                        = "Mean Evalations",
       y                        = "Count")
  theme_minimal()

p3 <- ggplot(data_processed_after_exclusions, aes(x = mean_evaluation, fill = gender)) +
  geom_histogram(alpha    = 0.5,
                  position = "dodge",
                 )+#binwidth = 5,
                 # alpha    = 0.5,
                 # position = "dodge") +
  scale_x_continuous(breaks = pretty_breaks(n = 7)) +
  coord_cartesian(xlim = c(0, 7)) +
    scale_fill_discrete(name      = "Gender",
                      labels    = c("Female",
                                    "Male",
                                    "Non-Binary"))+
  labs(title                    = "Histogram",
       x                        = "Mean Evalations",
       y                        = "Count") +
  facet_grid(~gender)+
  theme_minimal()

combined_plots <- p1 + p2 + p3

combined_plots

```


## Saving plots

Save plots to disk with `ggsave()`

\TODO Save the above combined plot to disk as both .png and .pdf. Ensure the png has at least 300dpi resolution.

```{r}

ggsave("combined_plots.png", combined_plots, path = "../data/processed/", width = 20, height = 10)

```


# Session info

```{r}

sessionInfo()

```



