---
title: "Evaluations the relationship between the big-5 personality facets and implicit racial attitudes"
subtitle: "Analysis"
author: "Andreas Szukics"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
 html_document:
    # code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
    css: styles.css  # CSS file for costumized html
---

```{r, include=FALSE}

# set knit options
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

# disable scientific notation
options(scipen = 999) 

```

# Libraries

```{r, echo = FALSE}

library(tidyverse)
library(knitr)
library(kableExtra)
library(janitor)
library(ltm)
library(scales)
library(PupillometryR)
library(palmerpenguins)
library(ggdist)
library(ggExtra)
library(ggrepel)
library(remotes)
library(ggthemes)
library(ggsci)
# devtools::install_github("psyteachr/introdataviz")

```


# Data

## Load the processed data 

```{r, echo = FALSE}

# Loading data
data_processed <- read_csv("../data/processed/data_processed.csv")

```


# Descriptive tables

## Sample size before exclusions

```{r}

data_processed |>
  count(name = "n") |>
  kable() |>
  add_header_above(header = c("Whole sample" = 1)) |> # note that you can add header rows to tables like this. The "1" indicates the number of columns the header should span. The sum of these numbers must equal the number of columns or you'll get an error.
  kable_classic(full_width = FALSE)

```


## Dataframe without excluded subject

```{r}

# Loading only subject to be included
data_processed_after_exclusions <- data_processed |>
  filter(exclude_participant == "include")

```


## Sample size after exclusions

Sample used in subsequent analyses

```{r}

data_processed_after_exclusions |>
  count(name = "n") |>
  kable() |>
  add_header_above(header = c("For analysis" = 1)) |>
  kable_classic(full_width = FALSE)

```


## Age

```{r}

data_processed_after_exclusions |>
  mutate(age = as.numeric(age)) |>
  summarise(Mean = mean(age, na.rm = TRUE),
            SD = sd(age, na.rm = TRUE)) |>
  mutate_all(.funs = janitor::round_half_up, digits = 1) |>
  kable() |>
  add_header_above(header = c("Age" = 2)) |>
  kable_classic(full_width = FALSE)

```


## Gender

```{r}

data_processed_after_exclusions |> 
  rename(Gender = gender) |>
  group_by(Gender) |> 
  summarise(n = n()) |> 
  mutate(Percent = paste0(round_half_up((n / sum(n)) * 100, 1), "%")) |>
  mutate(Gender = stringr::str_to_sentence(Gender)) |> # Change the case of the Gender variable so that it prints nicely
  kable() |>
  kable_classic(full_width = FALSE)

```


# Descriptive statistics

## Cronbach alpha calculation

```{r}

# List of subscales
subscales <- c("a", "c", "e", "n", "o")
num_items <- c(9, 9, 8, 8, 10)

# Empty list to store Cronbach's alpha values
cronbach_alphas <- list()

# Loop to compute Cronbach's alpha for each subscale
for (i in seq_along(subscales)) {
    # Generate column names for the current subscale
    selected_columns <- paste0("bfi_", subscales[i], 1:num_items[i])
  
    # Filter rows where all items in the subscale are complete (no NAs)
    # Using a standard subsetting approach instead of all_of
    dat_subscale <- data_processed_after_exclusions[, selected_columns, drop = FALSE] |>
                    na.omit()

    # Check if the subscale has sufficient data for alpha calculation
    if(nrow(dat_subscale) > 1) {
        # Compute Cronbach's alpha
        alpha_subscale <- cronbach.alpha(dat_subscale)$alpha
    } else {
        alpha_subscale <- NA  # Assign NA if not enough data
    }
  
    # Store the alpha coefficient in the list
    cronbach_alphas[[subscales[i]]] <- alpha_subscale
}

# Print Cronbach's alpha values
print(cronbach_alphas)


```

# Plotting

## Histogramms

### BFI subscale

```{r}
# Theme for all plots
# theme_set()

#BFI A
ggplot(data_processed_after_exclusions, aes(x = mean_a)) +
  geom_histogram(position = "dodge",
                 binwidth = .1,
                 fill     = "lightblue",
                 color    = "black")+
  geom_density(alpha = 0.5, fill = "orange") +
  geom_vline(aes(xintercept = mean(mean_a, na.rm = TRUE)), 
             linetype = "dashed", color = "red", size = 1) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 15)) +
  coord_cartesian(xlim = c(1, 6), ylim = c(1, 15)) +
  labs(title           = "BFI mean score",
       subtitle        = "Subscale A",
       x               = "Mean score",
       y               = "Count") +
   theme_classic() +
  # Make the axis label bold
  theme(plot.title    = element_text(color = "#0099F8", size = 16, face = "bold"),
        plot.subtitle = element_text(size = 10, face = "bold"),
        axis.title.x  = element_text(face = "bold"),
        axis.title.y  = element_text(face = "bold"))

#BFI C
ggplot(data_processed_after_exclusions, aes(x = mean_c)) +
  geom_histogram(position = "dodge",
                 binwidth = .1,
                 fill     = "lightblue",
                 color    = "black")+
  geom_density(alpha = 0.5, fill = "orange") +
  geom_vline(aes(xintercept = mean(mean_c, na.rm = TRUE)), 
             linetype = "dashed", color = "red", size = 1) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 15)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 15)) +
  coord_cartesian(xlim = c(1, 6), ylim = c(1, 15)) +
  labs(title           = "BFI mean score",
       subtitle        = "Subscale C",
       x               = "Mean score",
       y               = "Count") +
   theme_test() +
  # Make the axis label bold
  theme(plot.title    = element_text(color = "#0099F8", size = 16, face = "bold"),
        plot.subtitle = element_text(size = 10, face = "bold"),
        axis.title.x  = element_text(face = "bold"),
        axis.title.y  = element_text(face = "bold"))

#BFI  E
ggplot(data_processed_after_exclusions, aes(x = mean_e)) +
  geom_histogram(position = "dodge",
                 binwidth = .1,
                 fill     = "lightblue",
                 color    = "black")+
  geom_density(alpha = 0.5, fill = "orange") +
  geom_vline(aes(xintercept = mean(mean_e, na.rm = TRUE)), 
             linetype = "dashed", color = "red", size = 1) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 15)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 15)) +
  coord_cartesian(xlim = c(1, 6), ylim = c(1, 15)) +
  labs(title           = "BFI mean score",
       subtitle        = "Subscale E",
       x               = "Mean score",
       y               = "Count") +
   theme_ggdist() +
  # Make the axis label bold
  theme(plot.title    = element_text(color = "#0099F8", size = 16, face = "bold"),
        plot.subtitle = element_text(size = 10, face = "bold"),
        axis.title.x  = element_text(face = "bold"),
        axis.title.y  = element_text(face = "bold"))

#BFI N
ggplot(data_processed_after_exclusions, aes(x = mean_n)) +
  geom_histogram(position = "dodge",
                 binwidth = .1,
                 fill     = "lightblue",
                 color    = "black")+
  geom_density(alpha = 0.5, fill = "orange") +
  geom_vline(aes(xintercept = mean(mean_n, na.rm = TRUE)), 
             linetype = "dashed", color = "red", size = 1) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 15)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 15)) +
  coord_cartesian(xlim = c(1, 6), ylim = c(1, 15)) +
  labs(title           = "BFI mean score",
       subtitle        = "Subscale N",
       x               = "Mean score",
       y               = "Count") +
   theme_clean() +
  # Make the axis label bold
  theme(plot.title    = element_text(color = "#0099F8", size = 16, face = "bold"),
        plot.subtitle = element_text(size = 10, face = "bold"),
        axis.title.x  = element_text(face = "bold"),
        axis.title.y  = element_text(face = "bold"))

#BFI O
ggplot(data_processed_after_exclusions, aes(x = mean_o)) +
  geom_histogram(position = "dodge",
                 binwidth = .1,
                 fill     = "lightblue",
                 color    = "black")+
  geom_density(alpha = 0.5, fill = "orange") +
  geom_vline(aes(xintercept = mean(mean_o, na.rm = TRUE)), 
             linetype = "dashed", color = "red", size = 1) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 15)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 15)) +
  coord_cartesian(xlim = c(1, 6), ylim = c(1, 15)) +
  labs(title           = "BFI mean score",
       subtitle        = "Subscale O",
       x               = "Mean score",
       y               = "Count") +
  theme_calc() +
  # Make the axis label bold
  theme(plot.title    = element_text(color = "#0099F8", size = 16, face = "bold"),
        plot.subtitle = element_text(size = 10, face = "bold"),
        axis.title.x  = element_text(face = "bold"),
        axis.title.y  = element_text(face = "bold"))


```


### IAT

```{r}

#IAT D
ggplot(data_processed_after_exclusions, aes(x = D)) +
  geom_histogram(position = "dodge",
                 binwidth = .05,
                 fill     = "lightblue",
                 color    = "black")+
  geom_density(alpha = 0.5, fill = "orange") +
  geom_vline(aes(xintercept = mean(D, na.rm = TRUE)), 
             linetype = "dashed", color = "red", size = 1) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 15)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 15)) +
  coord_cartesian(xlim = c(-1, .5), ylim = c(1, 15)) +
  labs(title           = "Implicit Association Test",
       subtitle        = "Greenwald \"D\" score",
       x               = "D score",
       y               = "Count") +
  theme_classic() +
  # Labs
  theme(plot.title    = element_text(color = "#0099F8", size = 16, face = "bold"),
        plot.subtitle = element_text(size = 10, face = "bold"),
        axis.title.x  = element_text(face = "bold"),
        axis.title.y  = element_text(face = "bold"))
```


## AMP evaluations

### Descriptive stats

\TODO add table of means, SDs, Ns

```{r}

# overall AMP score
dat_amp_score <- data_processed_after_exclusions |>
  summarise(Mean = mean(AMP_score, na.rm = TRUE),
            SD = sd(AMP_score, na.rm = TRUE),
            n = n()) |>
  mutate(group = "Full sample")

# self-reported evaluations by gender category
dat_amp_score_by_gender <- data_processed_after_exclusions |>
  group_by(group = gender) |>
  summarise(Mean = mean(AMP_score, na.rm = TRUE),
            SD = sd(AMP_score, na.rm = TRUE),
            n = n())

# combine both into one table
bind_rows(dat_amp_score,
          dat_amp_score_by_gender) |>
  select(Subset = group, Mean, SD, n) |> # select variables of interest, and rename one 
  mutate(Subset = stringr::str_to_sentence(Subset)) |> # Change the case of the Subset variable so that it prints nicely
  mutate_if(is.numeric, round_half_up, digits = 2) |>
  kable() |>
  add_header_above(header = c(" " = 1, "Self-reported evaluations" = 3)) |>
  kable_classic(full_width = FALSE)

```


### Descriptive plots

```{r}

ggplot(data_processed_after_exclusions, aes(x = AMP_score)) +
  geom_histogram(binwidth = 0.05,
                 fill =  "lightblue", 
                 color = "black") + 
  scale_colour_viridis_d(option = "plasma") +
  scale_x_continuous(breaks = pretty_breaks(n = 10)) +
  xlab("AMP score") +
  ylab("Frequency") +
  theme_clean()

```


# Analyses & hypothesis tests

## Self-reported evaluations are correlated with evaluations on the AMP

### Plot

```{r}

ggplot(data_processed_after_exclusions, aes(x = AMP_score, y = mean_evaluation)) +
  geom_jitter(shape = 21,
              color = "black",
              alpha = 1,
              fill = "violet") +
  geom_smooth(method = "lm",
              color = "blue") +
  xlab("AMP score") +
  ylab("Mean self-reported evaluation") +
  theme_clean() 

```


More complex plots:

#### Axial hisograms

Scatter plots with axial histograms using ggExtra: https://cran.r-project.org/web/packages/ggExtra/vignettes/ggExtra.html

\TODO add axial histograms to a scatter plot. Split both the scatter plot and the histograms by gender.
# move legend location!!!!!!!!!!

```{r}

# move legend location!!!!!!!

piris <- ggplot(data_processed_after_exclusions, aes(x = AMP_score, y = mean_evaluation, colour = gender)) +
  geom_point() +
  scale_y_continuous(breaks = pretty_breaks(n = 7)) +
  coord_cartesian(ylim = c(0, 7)) +
  xlab("AMP score") +
  ylab("Mean self-reported evaluation") +
  theme_light()+
  theme(legend.position = c(0.125,.7))

piris2 <- ggplot(data_processed_after_exclusions, aes(x = AMP_score, y = mean_evaluation, colour = gender)) +
  geom_point() +
  scale_y_continuous(breaks = pretty_breaks(n = 7)) +
  coord_cartesian(ylim = c(0, 7)) +
  xlab("AMP score") +
  ylab("Mean self-reported evaluation") +
  theme_light()+
  theme(legend.position = "bottom")

ggMarginal(piris, type = "histogram",groupColour = TRUE, groupFill = TRUE) 
ggMarginal(piris2, groupColour = TRUE, groupFill = TRUE)
```


#### Labelled points

Label points using ggrepel: https://cran.r-project.org/web/packages/ggrepel/vignettes/ggrepel.html

\TODO Label the points in a scatter plot using their participant codes.

```{r}

# repel <- 
ggplot(data_processed_after_exclusions, aes(x = AMP_score, y = mean_evaluation, label = subject, colour = gender)) +
  geom_point() +
  theme_minimal() +
  xlab("AMP score") +
  ylab("Mean self-reported evaluation") +
  geom_text_repel()

```


#### Magnify areas

Magnify areas of your plot with ggmagnify: https://hughjonesd.github.io/ggmagnify/

\TODO Magnify an area of one of your scatter plots, eg., where there are a lot of data points in a small area.

```{r}

library(ggmagnify)

ggp <- ggplot(data_processed_after_exclusions, aes(AMP_score, mean_evaluation, label = subject, colour = gender)) + 
  geom_point() +
  scale_y_continuous(breaks = pretty_breaks(n = 7)) +
  coord_cartesian(ylim = c(1, 7)) +
  xlab("AMP score") +
  ylab("Mean self-reported evaluation") +
  theme_clean()#+
  # geom_text_repel()

ggp

from <- c(xmin = 0.4, xmax = 0.6, ymin = 1.6, ymax = 3.4)
# Names xmin, xmax, ymin, ymax are optional:
to <- c(0.6,  1, 4, 7)

ggp + geom_magnify(from = from, to = to)

```


### Test

\TODO run an appropriate test. Below the output, interpret the results: write a few sentences that report and interpret the results following APA reporting style.

```{r}


# Fit the linear model
model_mean_amp <- lm(mean_evaluation ~ AMP_score, data = data_processed_after_exclusions)
summary(model_mean_amp)

```
I performed a linear regression analysis to see whether there was a correlation between mean evaluation and AMP score. The results show that there isn't any relation between the two variables (p > 0.05). Furthermore, the model does not seem to explain very little variance for mean evaluation.


## Self-reported evalautions differ between men and women

### Plot

\TODO split histogram, split violin plot, raincloud plot, etc.

```{r}

#histogramm

ggplot(data_processed_after_exclusions, aes(x = mean_evaluation, fill = gender)) +
  geom_histogram(alpha    = 0.5, 
                 position = "dodge",
                 binwidth = .2)+
                 # alpha    = 0.5, 
                 # position = "dodge") +
  scale_x_continuous(breaks = pretty_breaks(n = 7)) +
  coord_cartesian(xlim = c(0, 7)) +
  theme_minimal()

ggplot(data_processed_after_exclusions, aes(x = mean_evaluation, fill = gender)) +
  geom_histogram(alpha    = 0.5, 
                  position = "dodge",
                 )+#binwidth = 5,
                 # alpha    = 0.5, 
                 # position = "dodge") +
  scale_x_continuous(breaks = pretty_breaks(n = 7)) +
  coord_cartesian(xlim = c(0, 7)) +
  facet_grid(~gender)+
  theme_minimal()

#violin

ggplot(data_processed_after_exclusions, aes(x    = gender, y    = mean_evaluation, fill = gender)) +
  geom_flat_violin(draw_quantiles = .5, 
              trim           = TRUE,
              alpha          = 0.5,) +
  scale_y_continuous(breaks  = pretty_breaks(n = 7)) +
  coord_cartesian(ylim       = c(0, 7)) +
  theme_minimal()

#raincloud

ggplot(data_processed_after_exclusions, aes(x = gender, y = mean_evaluation, fill = gender)) +
  geom_boxplot(width         = 0.1,
               outlier.shape = NA,
               position      = position_nudge(x      = -0.2),
               alpha         = .7) +
  geom_point(position        = position_jitter(width = .1),
             aes(color       = gender),
             alpha           = .75,
             color           = "black",
             shape           = 21) +
  geom_flat_violin(trim=FALSE,
                   alpha = 0.4,
                   position = position_nudge(x = .2)) +
  scale_y_continuous(breaks  = pretty_breaks(n = 7)) +
  coord_cartesian(ylim       = c(0, 7)) +
  theme_minimal()

```


### Test

\TODO run an appropriate test. Below the output, interpret the results: write a few sentences that report and interpret the results following APA reporting style.

```{r}

data_processed_after_exclusions$gender_numeric <- ifelse(data_processed_after_exclusions$gender == "male", 1, 0)

# Fit the linear model
model_gender <- lm(mean_evaluation ~ gender_numeric, data = data_processed_after_exclusions)
summary(model_gender)

```

I also performed a linear regression test here to see whether there is a difference between gender in mean evaluation. There although the males have a higher average there seems to be no difference between the two genders (p > .109). 


## Evaluations on the Affect Misattribution Procedure differ between men and women

### Plot

\TODO split histogram, split violin plot, raincloud plot, etc.

This time, vary the labeling and order of the legend, e.g., capitalise "Men" and "Women", and know how to change the order of the factors.

```{r}

data_processed_after_exclusions$gender <- factor(data_processed_after_exclusions$gender, levels = c("nonbinary", "male", "female"))

#histogramm

ggplot(data_processed_after_exclusions, aes(x = mean_evaluation, fill = gender)) +
  geom_histogram(alpha    = 0.5, 
                 position = "dodge",
                 binwidth = .2)+
                 # alpha    = 0.5, 
                 # position = "dodge") +
  scale_x_continuous(breaks = pretty_breaks(n = 7)) +
  coord_cartesian(xlim = c(0, 7)) +
    scale_fill_discrete(name      = "Gender",
                      labels    = c("Non-Binary",
                                    "Man",
                                    "Woman"))+
  labs(title                    = "Histogram",
       x                        = "Mean Evalations",
       y                        = "Count") +
  theme_minimal()

ggplot(data_processed_after_exclusions, aes(x = mean_evaluation, fill = gender)) +
  geom_histogram(alpha    = 0.5, 
                  position = "dodge",
                 )+#binwidth = 5,
                 # alpha    = 0.5, 
                 # position = "dodge") +
  scale_x_continuous(breaks = pretty_breaks(n = 7)) +
  coord_cartesian(xlim = c(0, 7)) +
    scale_fill_discrete(name      = "Gender",
                      labels    = c("Non-Binary",
                                    "Man",
                                    "Woman"))+
  labs(title                    = "Histogram",
       x                        = "Mean Evalations",
       y                        = "Count") +
  facet_grid(~gender)+
  theme_minimal()

#violin

ggplot(data_processed_after_exclusions, aes(x    = gender, y    = mean_evaluation, fill = gender)) +
  geom_flat_violin(draw_quantiles = .5, 
              trim           = TRUE,
              alpha          = 0.5,) +
  scale_y_continuous(breaks  = pretty_breaks(n = 7)) +
  coord_cartesian(ylim       = c(0, 7)) +
    scale_fill_discrete(name      = "Gender",
                      labels    = c("Non-Binary",
                                    "Man",
                                    "Woman"))+
  labs(title                    = "Histogram",
       x                        = "Mean Evalations",
       y                        = "Count") +
  theme_minimal()

#raincloud

rain_height <- .1

ggplot(data_processed_after_exclusions, aes(x = gender, y = mean_evaluation, fill = gender)) +
  geom_boxplot(width         = 0.1,
               outlier.shape = NA,
               position      = position_nudge(x      = -0.2),
               alpha         = .7) +
  geom_point(position        = position_jitter(width = .1),
             aes(color       = gender),
             alpha           = .75,
             color           = "black",
             shape           = 21) +
  geom_flat_violin(trim=FALSE, alpha = 0.4,
  position = position_nudge(x = rain_height+.05)) +
  scale_y_continuous(breaks  = pretty_breaks(n = 7)) +
  coord_cartesian(ylim       = c(0, 7)) +
    scale_fill_discrete(name      = "Gender",
                      labels    = c("Non-Binary",
                                    "Man",
                                    "Woman"))+
  labs(title                    = "Raincloud Plot",
       x                        = "Gender",
       y                        = "Mean Evalations") +
  theme_minimal()


```


### Test

\TODO run an appropriate test. Below the output, print an interpretation of the results generated by the 'easystats' package [report](https://easystats.github.io/report/). I.e., use `report::report()`.

```{r}

# install.packages("report")
# install.packages("remotes")
# remotes::install_github("easystats/report") # You only need to do that once
library(report)

model_amp <- lm(AMP_score ~ gender_numeric, data = data_processed_after_exclusions)
report(model_amp)

```


## Combining plots

Combine plots using the library [patchwork](https://patchwork.data-imaginist.com/).

\TODO Combine at least three of the above plots into one.

```{r}

# # install.packages("devtools")
# devtools::install_github("thomasp85/patchwork")


library(patchwork)

p1 <- ggplot(data_processed_after_exclusions, aes(x = gender, y = mean_evaluation, fill = gender)) +
  geom_boxplot(width         = 0.1,
               outlier.shape = NA,
               position      = position_nudge(x      = -0.2),
               alpha         = .7) +
  geom_point(position        = position_jitter(width = .1),
             aes(color       = gender),
             alpha           = .75,
             color           = "black",
             shape           = 21) +
  geom_flat_violin(trim=FALSE, alpha = 0.4,
  position = position_nudge(x = rain_height+.05)) +
  scale_y_continuous(breaks  = pretty_breaks(n = 7)) +
  coord_cartesian(ylim       = c(0, 7)) +
     scale_fill_discrete(name      = "Gender",
                      labels    = c("Female",
                                    "Male",
                                    "Non-Binary"))+
  labs(title                    = "Raincloud Plot",
       x                        = "Gender",
       y                        = "Mean Evalations")
  theme_minimal()
p2 <- ggplot(data_processed_after_exclusions, aes(x    = gender, y    = mean_evaluation, fill = gender)) +
  geom_flat_violin(draw_quantiles = .5, 
              trim           = TRUE,
              alpha          = 0.5,) +
  scale_y_continuous(breaks  = pretty_breaks(n = 7)) +
  coord_cartesian(ylim       = c(0, 7)) +
   scale_fill_discrete(name      = "Gender",
                      labels    = c("Female",
                                    "Male",
                                    "Non-Binary"))+
  labs(title                    = "Violin Plot of Mean Evaluation",
       x                        = "Mean Evalations",
       y                        = "Count")
  theme_minimal()
  
p3 <- ggplot(data_processed_after_exclusions, aes(x = mean_evaluation, fill = gender)) +
  geom_histogram(alpha    = 0.5, 
                  position = "dodge",
                 )+#binwidth = 5,
                 # alpha    = 0.5, 
                 # position = "dodge") +
  scale_x_continuous(breaks = pretty_breaks(n = 7)) +
  coord_cartesian(xlim = c(0, 7)) +
    scale_fill_discrete(name      = "Gender",
                      labels    = c("Female",
                                    "Male",
                                    "Non-Binary"))+
  labs(title                    = "Histogram",
       x                        = "Mean Evalations",
       y                        = "Count") +
  facet_grid(~gender)+
  theme_minimal()

combined_plots <- p1 + p2 + p3

combined_plots

```


## Saving plots

Save plots to disk with `ggsave()`

\TODO Save the above combined plot to disk as both .png and .pdf. Ensure the png has at least 300dpi resolution.

```{r}

ggsave("combined_plots.png", combined_plots, path = "../data/processed/", width = 20, height = 10)

```


# Session info

```{r}

sessionInfo()

```



